Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Start to fomat the pseudocode as pseudocode in LaTeX.

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{breqn}

@@

input: l = position of light
	   r = the radius of each sphere and cylinder
	   spheres = a list of positions of centers of spheres
	   cylinders = a list of pairs of positions specifying the end faces of the
					cylinders
output: pixels = array of black and white pixels indicating on which areas of the
					wall light is incident

initialize pixels to be uniformly white (illuminated)

@@

for each cylinder in cylinders:
	//similar to the above but cylinders cast different shaped shadows
	// ...
	This case is not handled by our code.

>>>>

\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{breqn}
\usepackage[]{algorithm2e}

@@

\begin{dmath*}
\vec{l} = position of light\\
\vec{r} = the radius of each sphere and cylinder\\
spheres = a list of positions of centers of spheres\\
cylinders = a list of pairs of positions specifying the end faces of the cylinders
\end{dmath*}

\begin{algorithm}[H]
\DontPrintSemicolon
 \KwData{$\vec{l}$ = position of light, $\vec{r}$ = the radius of each sphere and cylinder, $spheres$ = a list of positions of centers of spheres, $cylinders$ = a list of pairs of positions specifying the end faces of the cylinders}
 \KwResult{$pixels$ = array of black and white pixels indicating on which areas of the wall light is incident}
 $pixels \leftarrow$ a uniformly white (illuminated) image of the desired size\;
 \For{each sphere in spheres}{
  read current\;
  \eIf{understand}{
   go to next section\;
   current section becomes this one\;
   }{
   go back to the beginning of current section\;
  }
 }
 \For{each cylinder in cylinders}{
  \tcp*[h]{similar to the above but cylinders cast different}
  \tcp*[h]{shaped shadows}\\
  \tcp*[h]{This case is not handled by our code.}
 }
 \caption{first shadow rendering method}
\end{algorithm}

@@
